---
title: "Gun Control Chi-Square"
author: "Allison Horst"
date: "November 14, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm Allison and I'm adding some text here to see if my collaborators can get this file. 

It's Allison again, and I'm updating some text.
Blah blah blah

I'm the collaborator adding something...

Creator (Allison): 

Getting gc_df.csv data, loading the tidyverse, and getting some summary counts

```{r}

library(tidyverse)
gc_df <- read_csv("gc_df.csv")

get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)

rownames(get_guns) <- c("Female","Male")

```

I'm the Collaborator (Allison_2) and I am going to do chi-square. 

Is there a significant difference in gun control perspectives (as related to access to guns) for males and females?

Is there a significant association between sex and gun control recommendations?

Is perception of gun control access independent of sex?

Chi-Square
```{r}

guns_prop <- prop.table(as.matrix(get_guns), 1)
guns_prop

# Perform chi-square

guns_x2 <- chisq.test(get_guns)
guns_x2

```

Recommended gvmt action on gun access differs significantly for males and females ($\chi^2$(`r guns_x2$parameter`) = ...., p < 0.001)
